---
title: "206_5_part_1"
author: "Lydia Bleifuss"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
#Loading Packages
library(tidyverse)
library(pwr)
library(knitr)
library(plotly)
library(extrafont)
library(ggrepel)
library(kableExtra)
library(effsize)
library(dplyr)
library(vcdExtra)
library(car)
library(ggpubr)
library(ggplot2)
library(ggsignif)
library(xtable)
library(stargazer)
```

**Male and female graduate enrollment (1967 - 2015)** 

Compare trends in total graduate enrollment for males and females (including full-time/part-time and private/public universities) in the United States from 1967 - 2015.

Describe your results statistically, graphically and in text.

**Example from LOBSTER**

There is a significant association between observed gender and enrollment in grad school from 1967 - 2015 ($\chi^2${`r grad_chi$parameter`} = ???, *p* = ???). 



```{r}

#Graphic Analysis
enroll_graph <- ggplot(grad_total, aes(x = year))+
  geom_line(aes(y = total_males, color = "total_males"))+
  geom_line(aes(y = total_females, color = "total_females"))

enroll_graph

#Linear Regression

lm_females <- lm(grad_total$total_females ~ grad_total$year)
summary(lm_females)

lm_males <- lm(grad_total$total_males ~ grad_total$year)
summary(lm_males)

#Looking at Regression Residuals
plot(lm_females)

plot(lm_males)

#Plotting Linear Regression
grad_model_graph <- ggplot(grad_total, aes(x = year)) +
  geom_point(aes(y = total_males, color = "total_males")) +
  geom_smooth(aes(y = total_males), method = lm, se = TRUE, size = 0.5, color = "gray15") +
  geom_point(aes(y = total_females, color = "total_females")) +
  geom_smooth(aes(y = total_females), method = lm, se = TRUE, size = 0.5, color = "gray15") +
  theme_classic() +
  theme(legend.justification=c(1,0), legend.position=c(0.3,0.8)) +
  scale_x_continuous(expand = c(0,0), limits = c(1967, 2016)) +
  labs(x = "Year", y = "Graduate Enrollment")
grad_model_graph + labs(color = "Gender")


```

