---
title: "206_5_part_3"
author: "Lydia Bleifuss"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
#Loading Packages
library(tidyverse)
library(pwr)
library(knitr)
library(plotly)
library(extrafont)
library(ggrepel)
library(kableExtra)
library(effsize)
library(dplyr)
library(vcdExtra)
library(car)
library(ggpubr)
library(ggplot2)
library(ggsignif)
library(xtable)
library(stargazer)
library(reshape2)
library(RColorBrewer)

```

**Male and female salaries for starting postdoctoral and other employment positions (2015)** 

Compare median salaries for male and female doctorate recipients in 2015. 

Questions One: Does median salary differ significantly between male and female starting POSTDOC positions? 

Question Two: Does median salary differ significantly between male and female PhD recipients in NON-POSTDOC employment positions?

```{r}
#Read in data and explore.

median_salary <- read_csv("median_sal.csv")

#Males non-post_doc (employment)

hist_male_employ <- ggplot(median_salary, aes(x = male_employ))+
  geom_histogram(bins = 10)
hist_male_employ

qq_male_employ <- ggplot(median_salary, aes(sample = male_employ))+
  geom_qq()
qq_male_employ

#Females non-post_doc (employment)

hist_female_employ <- ggplot(median_salary, aes(x = female_employ))+
  geom_histogram(bins = 10)
hist_female_employ

qq_female_employ <- ggplot(median_salary, aes(sample = female_employ))+
  geom_qq()
qq_female_employ

#Males post_doc

hist_male_post <- ggplot(median_salary, aes(x = male_post))+
  geom_histogram(bins = 10)
hist_male_post

qq_male_post <- ggplot(median_salary, aes(sample = male_post))+
  geom_qq()
qq_male_post

#Females post_doc

hist_female_post <- ggplot(median_salary, aes(x = female_post))+
  geom_histogram(bins = 10)
hist_female_post

qq_female_post <- ggplot(median_salary, aes(sample = female_post))+
  geom_qq()
qq_female_post

#Looking not super well distributed (bell-curve/linear) Man-Whitney U acceptable?
```
```{r}
#Man-Whitney-U (Wilcox Test)

#Does median salary differ significantly between male and female starting POSTDOC positions?

test_post <- wilcox.test(median_salary$male_post, median_salary$female_post, paired = TRUE)

test_post

#Not significant p-value
#What does "cannot compute exact p-value with ties..." mean?
```



```{r}
#Man-Whitney-U (Wilcox Test)

#Question Two: Does median salary differ significantly between male and female PhD recipients in NON-POSTDOC employment positions?

test_employ <- wilcox.test(median_salary$male_employ, median_salary$female_employ, paired = TRUE)

test_employ

#P-value is significant
#Same error message....

```

```{r}
#Combining data for post_doc

data_all <- melt(median_salary[c('field', 'male_post', 'female_post', 'male_employ', 'female_employ')], id.vars = 1)

#New df for post_doc graph

post_df <- data_all %>% 
  filter(variable == "female_post" | variable == "male_post")

#New df for employ graph

employ_df <- data_all %>% 
  filter(variable == "female_employ" | variable == "male_employ")
```


```{r}
#Column graphs of median salary for each field in post_doc

post_graph <- ggplot(post_df, aes(x = field, y = value))+
  geom_col(aes(fill = variable), position = "dodge")+
  theme_classic()+
  scale_fill_manual(values = c("cadetblue3", "darkslategray4"),
                    name = "Group",
                    labels = c("Male Postdoctoral Study", "Female Postdoctoral Study"
                    ))+
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,70000),
                     breaks = seq(0,70000, by = 10000))+ 
  theme(axis.text.x = element_text(angle = 55, hjust = 1, size = 5))+
  labs(x = "Field of Study", y = "Median Salary ($)")
```

```{r}
#Column graphs of median salary for each field in employ

employ_graph <- ggplot(employ_df, aes(x = field, y = value))+
  geom_col(aes(fill = variable), position = "dodge")+
  scale_fill_manual(values = c("goldenrod3", "darkseagreen4"),
                    name = "Group",
                    labels = c("Male Postdoctoral Employment", "Female Postdoctoral Employment"))+
  theme_classic()+
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,125000),
                     breaks = seq(0,125000, by = 20000))+ 
  theme(axis.text.x = element_text(angle = 55, hjust = 1, size = 5))+
  labs(x = "Field of Study", y = "Median Salary ($)")
```

```{r}
colnames(data_all) <- c("Field", "GenderEmployment", "Salary")

box_plot <- ggplot(data_all, aes(x = GenderEmployment, y = Salary, fill = GenderEmployment))+
  geom_boxplot(show.legend = FALSE)+
  theme_classic()+
  scale_fill_manual(values = c("goldenrod3", "darkseagreen4", "cadetblue3", "darkslategray4"))+
  labs(y = "Median Salary Across Fields ($)", x = "Group")+
  scale_y_continuous(expand = c(0,0),
                     limits = c(30000,130000))+
  scale_x_discrete(labels = c("male_post" = "Male \nPost Doc \nStudy",
                              "female_post" = "Female \nPost Doc \nStudy",
                              "male_employ" = "Male \n Post Doc \nEmployment",
                              "female_employ" = "Female \n Post Doc \nEmployment"))
  
box_plot


```

