---
title: "206_5_part_3"
author: "Lydia Bleifuss"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
#Loading Packages
library(tidyverse)
library(pwr)
library(knitr)
library(plotly)
library(extrafont)
library(ggrepel)
library(kableExtra)
library(effsize)
library(dplyr)
library(vcdExtra)
library(car)
library(ggpubr)
library(ggplot2)
library(ggsignif)
library(xtable)
library(stargazer)
```

**Male and female salaries for starting postdoctoral and other employment positions (2015)** 

Compare median salaries for male and female doctorate recipients in 2015. 

Questions One: Does median salary differ significantly between male and female starting POSTDOC positions? 

Question Two: Does median salary differ significantly between male and female PhD recipients in NON-POSTDOC employment positions?

```{r}
#Read in data and explore.

median_salary <- read_csv("median_sal.csv")

#Males non-post_doc (employment)

hist_male_employ <- ggplot(median_salary, aes(x = male_employ))+
  geom_histogram(bins = 10)
hist_male_employ

qq_male_employ <- ggplot(median_salary, aes(sample = male_employ))+
  geom_qq()
qq_male_employ

#Females non-post_doc (employment)

hist_female_employ <- ggplot(median_salary, aes(x = female_employ))+
  geom_histogram(bins = 10)
hist_female_employ

qq_female_employ <- ggplot(median_salary, aes(sample = female_employ))+
  geom_qq()
qq_female_employ

#Males post_doc

hist_male_post <- ggplot(median_salary, aes(x = male_post))+
  geom_histogram(bins = 10)
hist_male_post

qq_male_post <- ggplot(median_salary, aes(sample = male_post))+
  geom_qq()
qq_male_post

#Females post_doc

hist_female_post <- ggplot(median_salary, aes(x = female_post))+
  geom_histogram(bins = 10)
hist_female_post

qq_female_post <- ggplot(median_salary, aes(sample = female_post))+
  geom_qq()
qq_female_post

#Looking not super well distributed (bell-curve/linear) Man-Whitney U acceptable?
```
```{r}
#Man-Whitney-U (Wilcox Test)

#Does median salary differ significantly between male and female starting POSTDOC positions?

test_post <- wilcox.test(median_salary$male_post, median_salary$female_post, paired = TRUE)

test_post

#Not significant p-value
#What does "cannot compute exact p-value with ties..." mean?
```



```{r}
#Man-Whitney-U (Wilcox Test)

#Question Two: Does median salary differ significantly between male and female PhD recipients in NON-POSTDOC employment positions?

test_employ <- wilcox.test(median_salary$male_employ, median_salary$female_employ, paired = TRUE)

test_employ

#P-value is significant
#Same error message....

```

