---
title: "206_assignment_5_part2"
author: "Camila Bobroff"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Shifts in female PhD recipients by field (1985, 2000, and 2015). Describe if and how there was a shift in PhDs awarded to females in four fields (Physical and Earth Sciences, Engineering, Education, and Humanities & Arts) in 1985, 2000, and 2015. Describe your results statistically, in a graph or table, and in text. Note: There are several ways that you can interpret this question. You are invited to decide which you think is/are most interesting. Just be really clear about what you are asking/answering in your report.

```{r}
#Load packages and read in data

library(tidyverse)
library(dplyr)
library(ggplot2)
library(kableExtra)

female_phd <- read_csv("female_phds.csv")
female_phd_prop <- read_csv("female_phd_prop.csv")
```

Look into how percentage of females change based on field in each year (group by field. Another way to look at it would be: how percentages of females change within each field per year (group by year)

```{r}
#Bar graph showing total phd degrees females earned per year based on field
phd_bar <- ggplot(female_phd, aes(fill = Field, x = Year, y = Degrees)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  scale_x_continuous(expand = c(0,0), breaks = seq(1985,2015, by = 15))+
  scale_y_continuous(expand = c(0,0))

phd_bar 

#Create a graph showing number of degrees in each field as a percentage of the whole?

```


Step 3: Chi-Square
```{r}
#Chi-Square
# Is there an association between degrees awarded to females per year?

#H0: There is no association between degrees awarded to females and year.
#HA: There is an association between degrees awarded to females and year.
chi_phd <- female_phd_prop %>% 
  select(-Field)

rownames(chi_phd) <- c("Physical sciences and earth sciences", "Engineering", "Education", "Humanities and arts")

size_prop <- prop.table(as.matrix(chi_phd), 1)

phd_x2 <- chisq.test(chi_phd)

#p-value<.001, so we reject the null. There is an association between PhDs awarded to women and year.
```

